\NAME: A framework for \\ Efficient Intrusion Detection\\ in the Internet of Things

### 2014-10-17 paper.tex
disabled flushend, causing issues on last page
started rewrite design + added remaining TODO’s

\usepackage{flushend}

@@

The DSL enables researchers to formally describe their ID algorithms, without
focusing on any specific language or platform. Given such formal descriptions
of ID algorithms, a code generator is now able to combine these, while avoiding
the sequential patterns/problems presented in listings
\ref{alg:id-algo-application} and \ref{alg:id-algo-pattern}. It can also target
different languages and platforms, while reusing a software library that
provides e.g. message parsing, network access wrapping,\dots

>>>>

% \usepackage{flushend}

@@

The DSL enables researchers to formally describe their ID algorithms, without
focusing on any specific language or platform. Given such formal descriptions
of ID algorithms, a code generator is now able to combine these, while avoiding
the problems arising from the sequential patterns/problems presented in
listings \ref{alg:id-algo-application} and \ref{alg:id-algo-pattern}. It can
also target different languages and platforms, while reusing a software library
that provides e.g. message parsing, network access wrapping,\dots
